\documentclass[9pt]{beamer}
\usetheme[headlinetitle,footlineauthor,onesection]{alta}
\usepackage{tikz}
\usepackage{mathtools}
\usepackage{amsmath}

\newcommand{\supp}{\mathrm{supp}}
\newcommand{\im}{\mathrm{Im}}

\newtheorem{conj}{Conjecture}[section]
\newtheorem{cor}{Corollary}[section]

\begin{document}
\title{Cosystoles and Cheeger Constants of the Simplex}
\subtitle{Defense of the Ph.D. thesis}
\author{Kai Renken} 
\date{\today} 

\frame{\titlepage} 

\frame{\frametitle{Table of contents}\tableofcontents}

\section{The classical Cheeger constant of a graph}

\frame{\frametitle{An intuitive approach}
\pause
The classical Cheeger constant intuitively measures the stability of a connected graph.
\pause
\input{Figure1.tex}
\pause
Deleting the one edge in the middle will give a disconnected graph, consisting of two connected components, the smallest of them consisting of 5 vertices.\\
\pause
The Cheeger constant of this graph is $\frac{1}{5}$.
}

\frame{\frametitle{The definition of the classical Cheeger constant}

\pause

\begin{Definition}
Let $G=(V,E)$ be a (simple) graph. Then the \textbf{Cheeger constant} of $G$ is defined by
\[
h(G)=\min\left\{\frac{|\delta(A)|}{|A|}:A\subset V, 1\leq |A|\leq\frac{|V|}{2}\right\},
\]
with $\delta(A)\coloneqq\{e=(v,w)\in E:v\in A,w\in V\setminus A\}$.
\end{Definition}
\pause
\input{Figure3.tex}

}

\frame{\frametitle{The classical Cheeger constant of the simplex}

\pause

Let $K_n$ be the complete graph on $n$ vertices (which is the $1$-skeleton of the standard simplex on $n$-vertices).

\pause

Then we have:
\[
h(K_n)=\left\lceil\frac{n}{2}\right\rceil
\]
as follows:\\
\pause
For any subset $A\subset [n]\coloneqq\{1,\ldots,n\}$ we have:
\pause
\[
\frac{|\delta(A)|}{|A|}=\frac{|A|(n-|A|)}{|A|}=n-|A|,
\]

\pause

so by $|A|\leq\frac{n}{2}$ we get:

\pause

\[
h(K_n)=n-\left\lfloor\frac{n}{2}\right\rfloor=\left\lceil\frac{n}{2}\right\rceil
\]

}

\section{Generalized Cheeger constants of the simplex}
\frame{\frametitle{Cosystoles and the cosystolic norm}

\pause
From now we consider all cochain groups with $\mathbb{Z}_2$-coefficients.
\pause

\begin{Definition}
Let $X$ be an (abstract) simplicial complex. Then the \textbf{norm} of a cochain $\varphi\in C^k(X)$ is defined by:
\[
\|\varphi\|\coloneqq |\supp(\varphi)|
\]
\pause
The \textbf{cosystolic norm} of a cochain $\varphi\in C^k(X)$ (for $k\geq 1$) is defined by:
\[
\|\varphi\|_{csy}\coloneqq \min\left\{\|\delta^{k-1}(\phi)+\varphi\|:\phi\in C^{k-1}(X)\right\}
\]
\pause
A cochain $\varphi\in C^k(X)$ is called a $k$-\textbf{cosystole}, if it satisfies $\|\varphi\|_{csy}=\|\varphi\|$.
\end{Definition}
}

\frame{\frametitle{Coboundary expansion and the $k$-th Cheeger constant}

\begin{Definition}
For a cochain $\varphi\in C^k(X)\setminus\im(\delta^{k-1})$ the quotient
\[
\|\varphi\|_{exp}\coloneqq \frac{\|\delta^k(\varphi)\|}{\|\varphi\|_{csy}}
\]
is called the \textbf{coboundary expansion} of $\varphi$ and
\pause
\[
h_k(X)\coloneqq \min_{\substack{\varphi\in C^k(X)\\\varphi\notin\im(\delta^{k-1})}}\|\varphi\|_{exp}
\]
is called the $k$-th \textbf{Cheeger constant} of $X$.\\
\pause
A cosystole $\varphi\in C^k(X)\setminus\im(\delta^{k-1})$ satisfying $\|\varphi\|_{exp}=h_k(X)$ is called a \textbf{Cheeger cosystole}.
\end{Definition}
}

\frame{\frametitle{Relations to the classical Cheeger constant}
\pause
The classical Cheeger constant of a graph can be considered as the $0$-th Cheeger constant by defining the cosystolic norm of a $0$-cochain $\varphi\in C^0(X)$ as 
\[
\|\varphi\|_{csy}\coloneqq\min\{|\supp(\varphi)|,|X^{(0)}|-|\supp(\varphi)|\}
\]
\pause
The classical Cheeger constant of a graph equals $0$ iff the graph is disconnected.\\
\pause
The $k$-th Cheeger constant of a simplicial complex $X$ equals $0$ iff the $k$-th cohomology group $H^k(X)$ is non-trivial.\\
}

\frame{\frametitle{Example: The $1$-cosystoles of $\Delta^{[6]}$}
\pause
Let $\Delta^{[n]}$ always denote the standard simplex on $n$ vertices.
\pause
\input{Figure2.tex}
}

\frame{\frametitle{Maximal cosystoles}
\pause
\begin{Definition}
Let $X$ be a simplicial complex and $1\leq k\leq \dim(X)$, then
\[
C_{max}(X,k)\coloneqq \max\left\{\|\varphi\|_{csy}:\varphi\in C^k(X)\right\}
\]
is the largest norm a $k$-cosystole in $X$ can attain.
\end{Definition}
}

\frame{\frametitle{The largest cosystoles of the simplex}
\pause
\begin{theorem}[Renken]
\[
C_{max}(\Delta^{[n]},1)=\binom{\left\lceil\frac{n}{2}\right\rceil}{2}+\binom{\left\lfloor\frac{n}{2}\right\rfloor}{2}
\]
\end{theorem}
}

\frame{\frametitle{Some values for higher dimensional Cheeger constants}
\pause
\begin{theorem}[Wallach, Meshulam]
Let $\Delta^{[n]}$ be the standard simplex on $n$ vertices and $1\leq k\leq n-2$, then we have:
\[
\frac{n}{k+2}\leq h_k(\Delta^{[n]})\leq\left\lceil\frac{n}{k+2}\right\rceil
\]
If $n$ is divisible by $k+2$, then we have:
\[
h_k(\Delta^{[n]})=\frac{n}{k+2}
\]
\end{theorem}
\pause
\begin{theorem}[Kozlov]
Let $n>2$ not be a power of $2$, then we have:
\[
h_1(\Delta^{[n]})=\frac{n}{3}
\]
\end{theorem}
}

\frame{\frametitle{The case when $n$ is a power of $2$}
\pause
\begin{theorem}[Kozlov]
Let $n$ be a power of $2$. Then we have:
\[
h_1(\Delta^{[n]})\leq\frac{n^3-4n}{3n^2-24}
\]
\end{theorem}
\pause
\begin{theorem}[Kozlov]
\[
h_1(\Delta^{[8]})>\frac{8}{3}
\]
\end{theorem}
\pause
\begin{theorem}[Renken]
\[
h_1(\Delta^{[16]})>\frac{16}{3}
\]
\end{theorem}
}
\frame{\frametitle{Hitting sets and hitting numbers}
\pause
\begin{Definition}
Let $V$ be some set and $\mathcal{F}\subseteq 2^V$ a family of subsets of $V$. A subset $P\subseteq V$ is called a \textbf{hitting set} of $\mathcal{F}$ if we have $P\cap F\neq\emptyset$ for all $F\in\mathcal{F}$. The \textbf{hitting number} of $\mathcal{F}$ is defined by
\[
\tau(\mathcal{F})\coloneqq\min\{|P|:P\subseteq V\text{ is a hitting set of }\mathcal{F}\}
\]
\pause
If $\mathcal{F}$ is a family of chains / cochains, the hitting sets and the hitting number of $\mathcal{F}$ are defined as the hitting sets and the hitting number of $\{\supp(\varphi):\varphi\in\mathcal{F}\}$.
\end{Definition}
\pause
\begin{Example}
Let $V\coloneqq \left\{1,2,3,4,5\right\}$ and $\mathcal{F}\coloneqq \left\{\{1,2\},\{2,3,4\},\{1,5\},\{2,4,5\}\right\}$, then we have $\tau(\mathcal{F})=2$.
\end{Example}
}

\frame{\frametitle{The cycle detection theorem}
\pause
\begin{theorem}[Kozlov]
Let $X$ be a simplicial complex, $k\geq 1$, and $\varphi\in C^k(X)$. Let now $\mathcal{F}=\left\{\alpha_1,\ldots,\alpha_t\right\}$ be a family of $k$-cycles in $C_k(X)$, such that $\left\langle\varphi,\alpha_i\right\rangle=1$ for all $1\leq i\leq t$, then we have:
\[
\|\varphi\|_{csy}\geq\tau(\mathcal{F})
\]
\end{theorem}
\pause
\begin{cor}[Kozlov]
Let $\varphi\in C^k(X)$ and $\mathcal{F}=\{\alpha_1,\ldots,\alpha_{\|\varphi\|}\}\subset C_k(X)$ be a family of $k$-cycles, such that their supports are pairwise disjoint and $\left\langle\varphi,\alpha_i\right\rangle=1$ for all $1\leq i\leq\|\varphi\|$, then $\varphi$ is a cosystole.
\end{cor}
}

\frame{\frametitle{The cycle detection theorem}
\pause
Question: Are all cosystoles detectable using the cycle detection theorem?\\
\pause
Answer: We can not prove it by now, but we also do not know any counterexample.\\
\pause
Question: Are all cosystoles detectable using disjoint cycles?\\
\pause
Answer: No. The following $1$-cosystole is not detectable this way:

\input{Figure4.tex} 

\pause
Conjecture: For every proper $n$ and $k$ there is a Cheeger cosystole in $C^k(\Delta^{[n]})$ which is detectable using disjoint cycles.
}

\section{Alternative generalizations of the classical Cheeger constant}

\frame{\frametitle{Disjoint cycle expansion}
\pause
\begin{Definition}
Let $X$ be a simplicial complex, $\mathcal{F}\subset C_k(X)$ a family of cycles, such that their supports are pairwise disjoint and
\footnotesize
\[
P(\mathcal{F})\coloneqq\{\varphi\in C^k(X):|\supp(\varphi)\cap\supp(F)|=1\text{ for all }F\in\mathcal{F}\text{ and }\supp(\varphi)\subset\bigcup\limits_{F\in\mathcal{F}}\supp(F)\}
\]
\normalsize
\pause
Then we define
\[
\gamma_{\mathcal{F}}\coloneqq\frac{\min\limits_{\varphi\in P(\mathcal{F})}\|\delta^k(\varphi)\|}{|\mathcal{F}|}
\]
\pause
and we call
\[
\gamma_k(X)\coloneqq\min\limits_{\mathcal{F}\in\mathfrak{C}}\gamma_{\mathcal{F}}
\]
the $k$-th \textbf{disjoint cycle expansion} of $X$ with
\footnotesize
\[
\mathfrak{C}\coloneqq\{\mathcal{F}\subset C_k(X):F\text{ is a cycle and }\supp(F)\cap\supp(F')=\emptyset\text{ for all }F,F'\in\mathcal{F}\:(F\neq F')\}
\]
\normalsize
\end{Definition}

}

\frame{\frametitle{Hitting expansion}
\pause
\begin{Definition}
Let $X$ be a simplicial complex, $\mathcal{F}\subset C_k(X)$ a family of cycles and
\[
P'(\mathcal{F})\coloneqq\{\varphi\in C^k(X):|\supp(\varphi)\cap\supp(F)|\text{ is odd for all }F\in\mathcal{F}\}
\]
\pause
Then we define
\[
\rho_{\mathcal{F}}\coloneqq\frac{\min\limits_{\varphi\in P'(\mathcal{F})}\|\delta^k(\varphi)\|}{\tau(\mathcal{F})}
\]
\pause
and we call
\[
\rho_k(X)\coloneqq\min\limits_{\mathcal{F}\in\mathfrak{C}}\rho_{\mathcal{F}}
\]
the $k$-th \textbf{hitting expansion} of $X$, with
\[
\mathfrak{C}\coloneqq\{\mathcal{F}\subset C_k(X):F\text{ is a cycle, for all }F\in\mathcal{F}\}
\]
\end{Definition}
}

\frame{\frametitle{Relations to the Cheeger constant}
\pause
\begin{theorem}[Kozlov]
Let $X$ be a simplicial complex and $k\geq 1$, then we have:
\[
h_k(X)\leq\rho_k(X)\leq\gamma_k(X)
\]
\end{theorem}
\pause
\begin{theorem}[Kozlov]
Let $k+2$ devide $n$, then we have:
\[
\gamma_k(\Delta^{[n]})=\rho_k(\Delta^{[n]})=\frac{n}{k+2}
\]
\end{theorem}
\pause
\begin{theorem}[Renken]
Let $n$ not be a power of $2$, then we have:
\[
\gamma_1(\Delta^{[n]})=\rho_1(\Delta^{[n]})=\frac{n}{3}
\] 
\end{theorem}
}

\section{Partitioning consecutive numbers}

\frame{\frametitle{Partitioning consecutive numbers - Introducing example}
\pause
There are four ways to display the number \(15\) as a sum of consecutive numbers, namely:
\[
1+2+3+4+5=4+5+6=7+8=15
\]
\pause
We already know that for an \(n\in\mathbb{N}\) there are as many ways to display \(n\) as a sum of consecutive numbers as many odd divisors \(n\) has.\\
\pause
Question: Is it possible to partition the summands of the longer sums, such that each part sums up to one of the summands of the shorter sums?\\
\pause
Answer: No! For example there is no way to display the number \(7\) as a sum of the numbers \(4,5,6\).\\
\pause
But it is always possible if the longer sum's first summand is \(1\).
}

\frame{\frametitle{A theorem about partitioning consecutive numbers}
\pause
\begin{theorem}[Renken]
Let \(n,a,b\in\mathbb{N}\) (\(b\geq a\)), such that \(\sum\limits_{i=1}^ni=\sum\limits_{i=a}^bi\), then for every \(a\leq t\leq b\) there exists a subset \(U_t\subseteq [n]\), such that \(U_i\cap U_j=\emptyset\) for all \(i\neq j\) and we have\\
\([n]=\bigcup\limits_{a\leq t\leq b}U_t\) and \(\sum\limits_{i\in U_t}i=t\).
\end{theorem}
}
\section*{Bibliography}
\frame{\frametitle{Bibliography}
\begin{thebibliography}{1}
\bibitem{1}
Dmitry N. Kozlov, \textit{The first Cheeger constant of a simplex}, Graphs and Combinatorics (2017) 33: 1543. https://doi.org/10.1007/s00373-017-1853-9
\bibitem{2}
N. Linial, R. Meshulam, \textit{Homological connectivity of random 2-complexes}, Combinatorica 26, 2006,
no. 4, 475-487
\bibitem{3}
M. Gromov, \textit{Singularities, expanders and topology of maps. Part 2. From combinatorics to topology
via algebraic isoperimetry}, Geom. Funct. Anal. 20, (2010), no. 2, 416-526.
\bibitem{4}
M. Wallach and R. Meshulam, \textit{Homological connectivity of random k-dimensional complexes}, Random Structures Algorithms 34, 2009, no. 3, 408–417
\bibitem{5} Dmitry N. Kozlov and Roy Meshulam, \textit{Quantitative aspects of acyclicity}, arXiv:1802.03210 [math.CO], 2018
\bibitem{6} J. J. Sylvester and F. Franklin, \textit{A Constructive Theory of Partitions, Arranged in Three Acts, an Interact and an Exodion}, American Journal of Mathematics
Vol. 5, No. 1 (1882), pp. 251-330
\end{thebibliography}
}
\end{document}
